Evaluating the Effects of Tracker Reliability and Field of View on a Target Following Task in Augmented Reality

### 2009-06-25 Paper/paper.tex

\begin{figure}[t]
	\centering
	\includegraphics[width=3in]{figures/augmentedroom.png}
	\caption{Overhead view of virtual room (approx. measure).  Participant is stationary in the center of the room, with initial orientation along ``user view'' arrow.  Top-hat's initial position is outside the front doorway, directly in the participant's view.}
\end{figure}

@@

We designed an experiment to study a target following task which makes use of X-ray vision through an augmented reality device.  We used an augmented reality simulation to make the experiment feasible.

@@

Decreased reliability in the head-based rendering, caused by periods of sensor dropout, adversely affects performance.  However, for our task, the performance decrease levels off at one second dropouts.  Preliminary analysis also shows no significant difference between having no dropouts and half second dropouts.  This suggests that below a certain length of dropouts, good level of performance can be maintained, provided that the field of view is large enough.  This threshold on the dropouts would change depending on what is being followed, but we expect the same pattern would appear in other target following scenarios.

Future work lies in further investigating the effect of the dropout length 
below the one second level.  Also, this work points to other interesting experiments which might test the interaction between reliability of the head-based rendering and other immersion components.

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=2.5in]{figures/augmentedroom.png}
	\caption{Overhead view of virtual room (approx. measure).  Participant is stationary in the center of the room, with initial orientation along ``user view'' arrow.  Top-hat's initial position is outside the front doorway, directly in the participant's view.}
\end{figure}

@@

We designed a AR experiment to study the effects of tracker reliability and field of view on a target following task.  We developed a virtual reality based AR simulation to enable control over these independent variables.

@@

Decreased reliability in the head-based rendering, caused by periods of sensor dropout, adversely affects performance.  However, the performance decrease levels off at one second dropouts.  Preliminary analysis also shows no significant difference between having no dropouts and half second dropouts.  This suggests that below a certain length of dropout time, good performance may be maintained, given a sufficiently large FOV.  This threshold on dropouts would change depending on the task at hand, but we expect the same pattern would arise in other target following scenarios.

Future work lies in further investigating the effect of the dropout length 
below the one second level.  Our work also suggests new experiments designed to test the interaction between reliability of the head-based rendering and various other immersion components.
